---
title: "Zero-Inflated Beta Model Summary"
output: html_document
---

```{r setup, include=FALSE}
# Load necessary libraries
library(brms)
library(broom)
library(knitr)
library(kableExtra)
``` 

```{r, echo=FALSE}
# Create a data frame with the regression coefficients and relevant statistics
poisson_summary <- data.frame(
  Parameter = c("Intercept", "distance_m", "TrafficLow"),
  Estimate = c(0.10, -0.01, 1.36),
  Est.Error = c(0.41, 0.00, 0.38),
  `l-95% CI` = c(-0.71, -0.01, 0.62),
  `u-95% CI` = c(0.86, -0.00, 2.11),
  Rhat = c(1.00, 1.00, 1.00),
  Bulk_ESS = c(2185, 3443, 1684),
  Tail_ESS = c(2724, 2714, 2086)
)

# Load knitr for table rendering
library(knitr)

# Display the summary table
kable(poisson_summary, caption = "Poisson Regression Coefficients Summary", 
      format = "pipe", digits = 2)


# Create a data frame with the model summary output, including further distributional parameters
zib_summary <- data.frame(
  Parameter = c("Intercept", "zi_Intercept", "distance_m", "TrafficLow", "zi_distance_m", "zi_TrafficLow", "phi"),
  Estimate = c(-1.06, -1.99, -0.00, -0.23, 0.04, -9.98, 2.69),
  Est.Error = c(0.72, 1.72, 0.01, 0.83, 0.02, 4.09, 1.09),
  `l-95% CI` = c(-2.49, -5.94, -0.01, -1.79, 0.01, -19.49, 1.07),
  `u-95% CI` = c(0.34, 1.01, 0.01, 1.44, 0.10, -3.81, 5.31),
  Rhat = c(1.00, 1.00, 1.00, 1.00, 1.00, 1.01, 1.00),
  Bulk_ESS = c(4032, 2508, 2958, 2459, 1669, 1034, 2839),
  Tail_ESS = c(2949, 1741, 3033, 2825, 1185, 1492, 2571)
)


# Display the table in Markdown format using knitr::kable()
knitr::kable(zib_summary, format = "markdown", col.names = c("Parameter", "Estimate", "Est.Error", "l-95% CI", "u-95% CI", "Rhat", "Bulk_ESS", "Tail_ESS"))